HO unification from object language to meta language

### 2024-03-28 paper/main.tex
macro for unif pb, mappings and links display

\usepackage{myTools}
\usepackage{macros}

@@

In order to activate a \linketa $l$, we need to implement new rules for the
\elpiIn{progress1} predicate. After passing under all the \elpiIn{abs}
constructors of $l$, there are two cases making a \linketa to progress, 1) \lhs
is instantiated to a rigid term 2) \rhs can be $\eta$-reduced to a term with
rigid head. If \lhs is instantiated to a rigid term $t$, by \cref{inv:subst-nf},
we know that $t$ does not contain any \maybeeta. Let $t'$ the right hand side,
if $t$ is a constant or a function application, then, $t'$, which by
construction has \elpiIn{lam} as head, should be an $\eta$-expansion. We are
therefore allowed to unify $\lambda x. t \appsep x$ (the $\eta$-expanded version
of $t$) with $t'$. Finally, if \lhs starts has \elpiIn{lam} as constructor, then
$t$ is not an $\eta$-expansion and therefore, $t$ can be unified with $t'$.

@@

\begin{description}
  \item[Unif problems:] $X = \lambda x.\lambda y.x, Z = f\appsep(\lambda x.x)$
  \item[Mappings:] $\mapping{F}{H}{2}$  
  \item[Links:] $l_1 = \linketaM{x}{Y_{x}}{\lambda y.H_{y~x}}$,\\
                $l_2 = \linketaM{}{X}{\lambda x.Y_{x}}$,\\
                $l_3 = \linketaM{}{Z}{\lambda x.f \appsep G_{x}~x}$\\
                $l_4 = \linketaM{x}{G_{x}}{\lambda y.H_{x~y}}$
\end{description}

>>>>

\usepackage{myTools}
\usepackage{macros}
\usepackage{enumitem}

@@

In order to activate a \linketa $l$, we need to implement new rules for the
\elpiIn{progress1} predicate. After passing under all the \elpiIn{abs}
constructors of $l$, there are two cases making a \linketa to progress, 1) \lhs
is instantiated to a rigid term 2) \rhs is no more a \maybeeta or it is a term
which can be reduced to a term with rigid head. 
If \lhs is instantiated to a rigid term $t$, by \cref{inv:subst-nf},
we know that $t$ does not contain any \maybeeta. Let $t'$ the right hand side,
if $t$ is a constant or a function application, then, $t'$, which by
construction has \elpiIn{lam} as head, should be an $\eta$-expansion. We are
therefore allowed to unify $\lambda x. t \appsep x$ (the $\eta$-expanded version
of $t$) with $t'$. Finally, if \lhs starts has \elpiIn{lam} as constructor, then
$t$ is not an $\eta$-expansion and therefore, $t$ can be unified with $t'$.

@@

\newcommand{\printMinipage}[1]{
  \listlength{#1}
  \foreach \x [count=\i] in #1
    {
      \begin{minipage}{2.8cm}
        $\x$ %
      \end{minipage}
      \ifthenelse{\equal{\i}{\thellength}}{}{
        \ifthenelse{\isodd{\i}}{|}{\\}
      }
    }
}

\newcommand{\printLinks}[3]{
  \noindent
  \begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Unif problems:}]
    \item[Unif problems:] \printMinipage{#1}
    \item[Mappings:] \printMinipage{#2}
    \item[Links:] \printMinipage{#3}
  \end{description}
}

\printLinks{{
  X = \lambda x.\lambda y.x, 
  Z = f\appsep(\lambda x.x)}}
  {{\mapping{F}{H}{2}}}{{
  \linketaM{x}{Y_{x}}{\lambda y.H_{y x}},
  \linketaM{\phantom{x}}{X}{\lambda x.Y_{x}},
  \linketaM{\phantom{x}}{Z}{\lambda x.f \appsep G_{x}~x},
  \linketaM{x}{G_{x}}{\lambda y.H_{x~y}}}}
